Modern BTree\\ techniques

### 2020-01-09 btree/presentation.tex
Prefix truncation

\tikzset{rum-node/.style={draw,circle,fill=white,minimum width=2cm}}
\tikzset{rum-extra-node/.style={rectangle, draw, dashed, rounded corners, fill=white }}
\tikzset{btree-key/.style={minimum height=1cm, pattern=north west lines, draw}}
\tikzset{btree-pointer/.style={minimum height=1cm, draw}}
\tikzset{btree-hide/.style={draw opacity=0, line width=0, pattern=none}}
\tikzset{btree-empty/.style={btree-pointer, dashed}}
\tikzset{btree-leaf/.style={fill=greenGood}}
\tikzset{btree-branch/.style={fill=gray!20}}
\tikzset{btree-line/.style={line width=0.5pt}}
\tikzset{btree-path/.style={btree-pointer, minimum width=0.8cm, fill=red, opacity=0.5}}
\tikzset{>=latex}
\tikzset{btree-high-key/.style={btree-key, pattern=crosshatch, pattern color=red, draw=red}}

@@

        \onslide<4>
        \begin{tikzpicture}[]
            \btreenodewithitems{1}{5}{4}{}{btree-leaf}
        \end{tikzpicture}

@@

    \end{center}
\end{frame}
\note{
    BerkleyDB, https://web.stanford.edu/class/cs276a/projects/docs/berkeleydb/api_c/db_set_bt_prefix.html
}

@@

    \begin{overprint}[8cm]
    \end{overprint}

@@

>>>>

\tikzset{rum-node/.style={draw,circle,fill=white,minimum width=2cm}}
\tikzset{rum-extra-node/.style={rectangle, draw, dashed, rounded corners, fill=white }}
\tikzset{btree-key/.style={minimum height=1cm, pattern=north west lines, draw}}
\tikzset{btree-pointer/.style={minimum height=1cm, draw}}
\tikzset{btree-hide/.style={draw opacity=0, line width=0, pattern=none}}
\tikzset{btree-empty/.style={btree-pointer, dashed}}
\tikzset{btree-leaf/.style={fill=greenGood}}
\tikzset{btree-branch/.style={fill=gray!20}}
\tikzset{btree-line/.style={line width=0.5pt}}
\tikzset{btree-path/.style={btree-pointer, minimum width=0.8cm, fill=red, opacity=0.5}}
\tikzset{>=latex}
\tikzset{btree-high-key/.style={btree-key, pattern=north west lines, pattern color=red, draw=red}}
\tikzset{btree-key-prefix/.style={btree-key, minimum height=0.2cm, fill=red, opacity=0.5}}
\tikzset{btree-key-compare/.style={btree-key, minimum height=0.6cm, fill=blue, opacity=0.5}}

@@

        \onslide<4>
        \begin{center}
        \begin{tikzpicture}[]
            \btreenodewithitems{1}{8}{5}{}{btree-leaf}
            \coordinate[below=1cm of key11] (start1);
            \coordinate[below=1cm of high-key1] (start2);
            \draw[->, btree-line, line width=1.5pt, shorten >= 2mm] (start1) -- (key11);
            \draw[->, btree-line, line width=1.5pt, shorten >= 2mm] (start2) -- (high-key1);
        \end{tikzpicture}
        \end{center}

        \onslide<5>
        \begin{center}
        \begin{tikzpicture}[]
            \btreenodewithitems{1}{8}{5}{}{btree-leaf}
            \foreach \i in {1,...,4}
            {
                \coordinate[below=1cm of key1\i] (start\i);
                \draw[->, btree-line, line width=1.5pt, shorten >= 2mm] (start\i) -- (key1\i);
            }
        \end{tikzpicture}
        \end{center}

@@

    \end{center}
\end{frame}
\note{
    BerkleyDB, https://web.stanford.edu/class/cs276a/projects/docs/berkeleydb/api_c/db_set_bt_prefix.html

    TODO: mark shared parts of keys in both situations
}

@@

    \begin{overprint}[8cm]
        \onslide<1>
        \begin{center}
        \begin{tikzpicture}[]
            \btreenodewithitems{1}{8}{5}{}{btree-leaf}
            \node[btree-key, below=1cm of key13.center] (compared) {};
        \end{tikzpicture}
        \end{center}

        \onslide<2>
        \begin{center}
        \begin{tikzpicture}[]
            \btreenodewithitems{1}{8}{5}{}{btree-leaf}
            \node[btree-key, below=1cm of key13.center] (compared) {};

            \node[btree-key-prefix, below=1cm of key13.center] (compared-prefix) {};
            \node[btree-key-prefix, below=-0.5cm of high-key1.center] (compared-high-key-prefix) {};
            \node[btree-key-prefix, below=-0.5cm of key11.center] (compared-first-key-prefix) {};
        \end{tikzpicture}
        \end{center}

        \onslide<3>
        \begin{center}
        \begin{tikzpicture}[]
            \btreenodewithitems{1}{8}{5}{}{btree-leaf}
            \node[btree-key, below=1cm of key13.center] (compared) {};

            \node[btree-key-prefix, below=1cm of key13.center] (compared-prefix) {};
            \node[btree-key-prefix, below=-0.5cm of high-key1.center] (compared-high-key-prefix) {};
            \node[btree-key-prefix, below=-0.5cm of key11.center] (compared-first-key-prefix) {};

            \node[btree-key-compare, below=-0.1cm of compared.center] (compare-key) {};
            \foreach \i in {1,...,4}
            {
                \node[btree-key-compare, below=-0.1cm of key1\i.center] (compare-\i) {};
            }
        \end{tikzpicture}
        \end{center}

@@

    \begin{center}
    \textbf{Suffix truncation}
    \vspace{1cm}

    \begin{overprint}[8cm]
    \end{overprint}
    \end{center}
